\documentclass[letter,11pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black,
}

\pagestyle{empty} 

\begin{document}

\noindent
\textbf{Abdul Saboor} \\
Department of Physics and Astronomy \\
University of Delaware, Newark, DE 19716 \\
\href{mailto:asaboor@udel.edu}{asaboor@udel.edu} \\
\href{tel:+13027227047}{(302) 722-7047}

\vspace{1cm}

\noindent
[Date]

\vspace{5mm}

\noindent
[Hiring Committee Chair Name, if known, otherwise use title] \\
[Chair's Title, e.g., Chair of the Search Committee] \\
[Department Name, e.g., Department of Physical Sciences] \\
[College/University Name] \\
[College/University Address]

\vspace{5mm}

\noindent
\textbf{Re: Application for [Position Title, e.g., Assistant Professor of Physics]}

\vspace{5mm}

\noindent
Dear [Dr./Professor Last Name or Search Committee Chair],

I am writing with great enthusiasm to apply for the [Position Title] position at [College/University Name], which I saw advertised on [Platform, e.g., HigherEdJobs.com]. As a Ph.D. candidate in Physics with a deep passion for undergraduate education and extensive experience across Physics, Mathematics, and Computer Science, I am confident that I possess the skills and dedication to make a significant contribution to your department. Your institution's commitment to [mention something specific, e.g., student-centered learning, undergraduate research, access to quality education] resonates deeply with my own professional philosophy.

Throughout my graduate studies, I have actively sought opportunities to develop as an educator. As detailed in my enclosed CV, I have served as a teaching assistant for a wide array of physics courses at the University of Delaware, from introductory algebra-based physics to advanced calculus-based courses for science majors. This experience has equipped me to explain complex concepts to students with diverse academic backgrounds and career goals. Furthermore, my work developing online lab curricula has prepared me to deliver high-quality instruction in both in-person and virtual environments.

My interdisciplinary background as a computational physicist provides a unique advantage in the classroom. I am not only prepared to teach the core physics and mathematics curriculum but am also highly qualified and eager to teach introductory computer science courses. My experience developing open-source Python packages allows me to move beyond theory and engage students with hands-on, project-based learning that builds practical, in-demand skills. As outlined in my teaching statement, I am passionate about using real-world applications and computational tools to demystify abstract topics and spark genuine curiosity in students.

I am excited by the prospect of joining a department that values excellent teaching and mentorship. I am eager to contribute by not only teaching a range of courses but also by mentoring students, potentially involving them in accessible computational research projects.

Thank you for considering my application. My CV and teaching statement are attached for your review. I look forward to the possibility of discussing how my dedication, experience, and enthusiasm can benefit the students and faculty at [College/University Name].

\vspace{5mm}

\noindent
Sincerely, \\
\vspace{1cm}
\noindent
Abdul Saboor

\end{document}