\documentclass[letter,11pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black,
}

\pagestyle{empty}

\begin{document}

\noindent
\textbf{Abdul Saboor} \\
Department of Physics and Astronomy \\
University of Delaware, Newark, DE 19716 \\
\href{mailto:asaboor@udel.edu}{asaboor@udel.edu} \\
\href{tel:+13027227047}{(302) 722-7047}

\vspace{5mm}

\noindent
\textbf{Re: Senior Test Engineer Position at Coherent Corp.}
\vspace{5mm}

\noindent
Dear Hiring Manager,

I am applying for the Senior Test Engineer position working on fiber optic modules at Coherent Corp. I am a Ph.D. candidate in Physics focusing on semiconductor materials, with extensive experience in Python programming, data analysis, and laboratory instrumentation. My technical background and problem-solving approach make me a strong fit for this role.

I have built and maintained several open-source Python packages, including \href{https://github.com/asaboor-gh/ipyvasp}{ipyvasp} for data processing of density functional theory (DFT) calculations and \href{https://github.com/asaboor-gh/ipyslides}{ipyslides} for creating interactive presentations in Jupyter. These projects show my ability to design tools that make complex data more accessible. I also have hands-on LabVIEW experience from teaching laboratory courses, which included working with test instruments and experimental data acquisition interfaces.

In my role as a teaching assistant, I have trained undergraduate engineering students in using electrical instruments and data acquisition software. This required writing clear procedures, producing accurate reports, and explaining technical concepts in ways that matched each student’s skill level.

As lead researcher on projects studying epitaxial strain effects and Bi incorporation in III-Vs, I managed multiple projects at once while developing creative approaches to technical challenges. That experience sharpened my ability to work independently, adapt to changing requirements, and keep quality high under time constraints.

Coherent Corp.'s work in photonics and optical technologies is exactly the type of environment where I want to apply my skills. I am excited about the chance to work on fiber optic module testing and contribute to both product development and quality assurance.

Thank you for reviewing my application. I welcome the opportunity to discuss how my background in programming, testing, and technical communication can support your team’s goals.

\vspace{5mm}

\noindent
Sincerely, \\
Abdul Saboor

\end{document}