% filepath: resume_industry_test_engineer.tex
\documentclass[letter,11pt]{article}
\usepackage[left=0.8in,right=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,      
    urlcolor=blue!80!black,
}

\urlstyle{same}

\titleformat{\section}{\large\bfseries\color{blue!60!black}}{}{0em}{} 

\begin{document}

\begin{minipage}{0.65\textwidth}
    \raggedright
    {\Large \textbf{ABDUL SABOOR}} \\ 
    Department of Physics and Astronomy, University of Delaware, Newark, DE 19716 
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
    \raggedright
    \faGithub \quad \href{https://github.com/asaboor-gh}{asaboor-gh}\\
    \faLinkedin \quad \href{https://linkedin.com/in/asaboor-in}{asaboor-in} \\
    \faPhone \quad \href{tel:+13027227047}{(302) 722-7047} \\
    \faEnvelope \quad \href{mailto:asaboor@udel.edu}{asaboor@udel.edu}
\end{minipage}
\vspace{2mm}
\hrule

\vspace{5mm} \noindent Graduate student specializing in semiconductor material modeling and electronic structure tuning using density functional theory (DFT). Experienced in Python programming, open-source package development, and advanced data analysis for materials research.

\section{Education}
\begin{tabular}{p{3.25cm} p{12cm}}
    \textbf{2026 (Expected)} & Ph.D. in Physics, University of Delaware, Newark, DE \\
    \textbf{2025} & M.S. in Physics, University of Delaware, Newark, DE \\
    \textbf{2017} & M.Phil. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2015} & M.Sc. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2012} & B.Sc. in Mathematics \& Physics, University of Azad Jammu \& Kashmir \\
\end{tabular}

\section{Research Experience}
\begin{itemize}
    \item Examined metal oxidation in IrO$_2$ in collaboration with an experimental team.
    \item Investigated band-gap engineering by Bi incorporation in III-V alloys for mid-infrared applications.
    \item Collaborated in the study of rare-earth monopnictide nanoparticles embedded in bismide III-V alloys and uniaxial strain effects in transition metal-dichalcogenides.
    \item Quantifying epitaxial strain effects on III-V materials as leading researcher.
\end{itemize}

\section{Technical Instruction \& Training}
\begin{itemize}
    \item Trained and mentored undergraduate engineering students in laboratory settings, including instruction on the use of electrical instruments and data acquisition software such as \textbf{LabVIEW} for the Fundamentals of Physics Laboratory II (PHYS 228) and Fundamentals of Physics with Biomedical Applications II (PHYS 204).
    \item Developed and delivered technical content for a variety of physics courses for remote instruction, effectively communicating complex topics to diverse audiences.
    \item Managed multiple lab sections and projects simultaneously, ensuring all objectives were met on schedule for courses including PHYS201, PHYS202 and PHYS207.
\end{itemize}


\section{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python (Expert), MATLAB, Mathematica
    \item \textbf{Scientific \& Lab Software:} \href{https://www.vasp.at/}{VASP} (Expert), \href{https://www.quantum-espresso.org/}{Quantum ESPRESSO}, \href{https://wiki.fysik.dtu.dk/ase/}{ASE}, \href{https://nanohub.org}{nanohub}, \href{https://kwant-project.org}{Kwant}, \href{https://axelvandewalle.github.io/www-avdw/atat/}{ATAT}, LabVIEW
    \item \textbf{Developer Tools:} Git, VS Code, Jupyter, Conda, Linux, PowerShell
    \item \textbf{Core Competencies:} Data Analysis, Technical Documentation, Resourceful Problem-Solving, Project Management, Technical Training
\end{itemize}

\section{Authored Open Source Software}
\begin{itemize}
    \item \href{https://github.com/asaboor-gh/ipyvasp}{ipyvasp}: A Python package for processing and analyzing VASP simulations.
    \item \href{https://github.com/asaboor-gh/ipyslides}{ipyslides} \& \href{https://github.com/asaboor-gh/einteract}{einteract}: Python packages for creating interactive presentations and dashboards in Jupyter Notebooks, highlighting skills in user interface design for effective presentations.
\end{itemize}

\section{Publications}
\begin{itemize}
    \item S. Nair, \textbf{A. Saboor}, et al.,``Engineering metal oxidation using epitaxial strain," \href{https://www.nature.com/articles/s41565-023-01397-0}{\textit{Nat. Nanotechnol.}, (2023)}
    \item \textbf{A. Saboor}, S. Khalid, A. Janotti, ``Band-gap reduction and band alignments of dilute bismide III-V alloys," \href{https://arxiv.org/abs/2411.19257}{\textit{arXiv:2411.19257} [cond-mat]} (2024)
    \item \textbf{A. Saboor}, ``ipyvasp: A Python Package for Interactive Analysis and Visualization of VASP Data". Zenodo, \href{https://zenodo.org/records/15482349}{\textit{DOI}: 10.5281/zenodo.15482349} (2025)
    \item \textbf{A. Saboor}, ``ipyslides: A Python Framework for Creating Interactive Presentations in Jupyter Notebooks", \href{https://zenodo.org/records/15482496}{\textit{DOI}: 10.5281/zenodo.15482496} (2025)
    \item I. Evangelista, I. Chatratin, R. Hu, D. Q. Ho, \textbf{A. Saboor}, M. Zubair, S. Khalid, I. Fampiou, and A. Janotti. ``Effects of uniaxial stress and biaxial strain on the electronic properties of
        monolayer transition-metal dichalcogenides." (submission ready)
    \item \textbf{A. Saboor}, R. Hu, and A. Janotti. ``Electronic properties of InAlAs and InGaAs alloys containing a few percent of Bi." (in progress)
    \item R. Hu, W. Acuna, \textbf{A. Saboor}, D. Q. Ho, J. Zide, G. W. Bryant, and A. Janotti. ``Rare-earth monopnictides nanoparticles embedded in bismide III-V alloys for THz devices." (in progress)
\end{itemize}

\section{Conference Presentations}
\begin{itemize}
    \item The 67$^{th}$ Electronic Materials Conference, Duke University NC, (2025) \\
      Presented: ``Electronic properties of InAlAs and InGaAs alloys containing a few percent of Bi"
    \item The Franklin Institute Awards Symposium, Temple University, (2025)
    \item PyCon US, Pittsburgh, (2025)
    \item American Physical Society (APS) March Meeting, Las Vegas, (2023) \\
      Presented: ``Electronic structure and band alignment of dilute III-V$_{1-x}$Bi$_x$ alloys"
\end{itemize}


\section{References}
\textbf{Prof. Anderson Janotti} \\
Department of Material Science and Engineering, University of Delaware \\
Email: \href{mailto:janotti@udel.edu}{janotti@udel.edu} \\
\vspace{2mm}

\noindent \textbf{John Shaw} \\
Assistant Professor and Lab Manager \\
Department of Physics and Astronomy, University of Delaware \\
Email: \href{mailto:jdshaw@udel.edu}{jdshaw@udel.edu}
\end{document}