\documentclass[letter,11pt]{article}
\usepackage[left=0.8in,right=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,      
    urlcolor=blue!80!black,
}

\urlstyle{same}

\titleformat{\section}{\large\bfseries\color{blue!60!black}}{}{0em}{} 

\begin{document}

\begin{minipage}{0.65\textwidth}
    \raggedright
    {\Large \textbf{ABDUL SABOOR}} \\ 
    Department of Physics and Astronomy, University of Delaware, Newark, DE 19716 
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
    \raggedright
    \faGithub \quad \href{https://github.com/asaboor-gh}{asaboor-gh}\\
    \faLinkedin \quad \href{https://linkedin.com/in/asaboor-in}{asaboor-in} \\
    \faPhone \quad \href{tel:+13027227047}{(302) 722-7047} \\
    \faEnvelope \quad \href{mailto:asaboor@udel.edu}{asaboor@udel.edu}
\end{minipage}
\vspace{2mm}
\hrule
\vspace{4mm} 

\noindent
\textbf{Summary:} Dedicated Physics Ph.D. candidate with a passion for undergraduate education. Combines extensive teaching and mentorship experience with a strong computational research background. Proven ability to develop engaging course content and a desire to bring modern research concepts into the classroom and involve students in scholarly activities. Seeking a teaching-focused position at an institution that values high-quality instruction and student success.

\section{Education}
\begin{tabular}{p{3.25cm} p{12cm}}
    \textbf{2026 (Expected)} & Ph.D. in Physics, University of Delaware, Newark, DE \\
    \textbf{2025} & M.S. in Physics, University of Delaware, Newark, DE \\
    \textbf{2017} & M.Phil. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2015} & M.Sc. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2012} & B.Sc. in Mathematics \& Physics, University of Azad Jammu \& Kashmir \\
\end{tabular}

\section{Teaching Experience}
\quad \textbf{University of Delaware} (2018 -- 2025)
\begin{itemize}
    \item[] Worked as a Teaching Assistant for a wide range of undergraduate physics courses over multiple semesters. Responsibilities included leading laboratory and discussion sessions, grading, holding office hours, developing online course materials, and providing one-on-one student support in the Physics Help Center. Courses and responsibilities include:
    \item \textbf{Introductory Physics I \& II (PHYS 201, PHYS 202)} (2018-2022) \\
        Led multiple laboratory sections, graded assignments and lab reports.
    \item \textbf{Fundamentals of Physics I \& II (PHYS 207, PHYS 208)} (2019-2023) \\
        Supervised laboratory sessions and graded lab reports for calculus-based physics for multiple majors.
    \item \textbf{Fundamentals of Physics with Biomedical Applications II (PHYS 204)} (2022-2024) \\
        Guided students with experiments tailored for biomedical applications, graded reports.
    \item \textbf{Physics Online Lab Development} (2020) \\
        Collaborated with faculty and TAs to design, create, and implement online laboratory content for undergraduate physics courses for remote learning.
    \item \textbf{Fundamentals of Physics Laboratory II (PHYS 228)} (2022-2025) \\
        Supervised discussion and laboratory sections, graded assignments, and provided one-on-one academic support to students.
    \item \textbf{Physics Help Center TA} (2018-2025) \\
        Provided drop-in academic support to undergraduate students in a wide range of introductory physics courses, assisting with problem-solving skills and conceptual understanding.
\end{itemize}
\vspace{2mm}
\quad \textbf{Quaid-i-Azam University} (2017)
\begin{itemize}
    \item[] Worked as a Physics Teaching Assistant for one semester, assisting with teaching, grading, and laboratory supervision for undergraduate computer science students.
\end{itemize}

\section{Research Experience}
\begin{itemize}
    \item Led large-scale DFT simulations to model the electronic and structural properties of novel semiconductor alloys, directly supporting the design of advanced memory systems and non-Von Neumann computing hardware.
    \item Engineered material properties, such as band-gaps and strain effects, in III-V alloys and 2D materials, providing foundational research for next-generation electronic devices.
    \item Authored and co-authored research papers for high-impact peer-reviewed journals, including \textit{Nature Nanotechnology}.
    \item Mentored fellow graduate students with coding for analysis in their research, fostering a collaborative and productive team environment.
\end{itemize}

\section{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, MATLAB, Mathematica, PowerShell, Julia (learning)
    \item \textbf{Scientific Software:} \href{https://www.vasp.at/}{VASP}, \href{https://www.quantum-espresso.org/}{Quantum ESPRESSO}, \href{https://wiki.fysik.dtu.dk/ase/}{ASE}, \href{https://nanohub.org}{nanohub}, \href{https://kwant-project.org}{Kwant}, \href{https://axelvandewalle.github.io/www-avdw/atat/}{ATAT}
    \item \textbf{Developer Tools:} Git, Jupyter, VS Code, Linux, Conda
    \item \textbf{Open Source Projects Authored:}
    \begin{itemize}
        \item \href{https://github.com/asaboor-gh/ipyvasp}{ipyvasp}, a Python package for automating and analyzing VASP simulations.
        \item \href{https://github.com/asaboor-gh/ipyslides}{ipyslides}, a tool for creating interactive presentations within Jupyter Notebooks.
        \item \href{https://github.com/asaboor-gh/einteract}{einteract}, a library for building interactive dashboards in Jupyter notebooks.
    \end{itemize}
\end{itemize}

\section{Publications}
\begin{itemize}
    \item S. Nair, \textbf{A. Saboor}, et al., ``Engineering metal oxidation using epitaxial strain," \href{https://www.nature.com/articles/s41565-023-01397-0}{\textit{Nat. Nanotechnol.}, (2023)}
    \item \textbf{A. Saboor}, S. Khalid, A. Janotti, ``Band-gap reduction and band alignments of dilute bismide III-V alloys," \href{https://arxiv.org/abs/2411.19257}{\textit{arXiv:2411.19257} [cond-mat]} (2024)
    \item \textbf{A. Saboor}, ``ipyvasp: A Python Package for Interactive Analysis and Visualization of VASP Data," Zenodo, \href{https://zenodo.org/records/15482349}{\textit doi: 10.5281/zenodo.15482349} (2025)
    \item \textbf{A. Saboor}, ``ipyslides: A Python Framework for Creating Interactive Presentations in Jupyter Notebooks," \href{https://zenodo.org/records/15482496}{\textit doi: 10.5281/zenodo.15482496} (2025)
    \item I. Evangelista, I. Chatratin, R. Hu, D. Q. Ho, \textbf{A. Saboor}, M. Zubair, S. Khalid, I. Fampiou, and A. Janotti. ``Effects of uniaxial stress and biaxial strain on the electronic properties of monolayer transition-metal dichalcogenides." (Submission ready)
    \item \textbf{A. Saboor}, R. Hu, and A. Janotti. ``Electronic properties of InAlAs and InGaAs alloys containing a few percent of Bi." (In progress)
    \item R. Hu, W. Acuna, \textbf{A. Saboor}, D. Q. Ho, J. Zide, G. W. Bryant, and A. Janotti. ``Rare-earth monopnictides nanoparticles embedded in bismide III-V alloys for THz devices." (In progress)
\end{itemize}

\section{Conference Presentations}
\begin{itemize}
    \item The 67$^{th}$ Electronic Materials Conference, Duke University NC, (2025) \\
      Presented: ``Electronic properties of InAlAs and InGaAs alloys containing a few percent of Bi"
    \item The Franklin Institute Awards Symposium, Temple University, (2025)
    \item PyCon US, Pittsburgh, (2025)
    \item American Physical Society (APS) March Meeting, Minneapolis, (2024) \\
      Presented (by advisor): ``Electronic properties of InAlAs and InGaAs alloys containing a few percent of Bi"
    \item American Physical Society (APS) March Meeting, Las Vegas, (2023) \\
      Presented: ``Electronic structure and band alignment of dilute III-V$_{1-x}$Bi$_x$ alloys"
    \item SCAN Workshop, Temple University, (2019)
\end{itemize}

\section{References}
\textbf{Prof. Anderson Janotti} \\
Department of Material Science and Engineering, University of Delaware \\
Email: \href{mailto:janotti@udel.edu}{janotti@udel.edu} \\

\noindent\textbf{John Shaw} \\
Assistant Professor and Lab Manager \\
Department of Physics and Astronomy, University of Delaware

\end{document}