\documentclass[letter,11pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black,
}

% No page numbers for a single-page statement
\pagestyle{empty} 

\begin{document}

\vspace{8mm}

\begin{center}
    \Large \textbf{Teaching Statement}
\end{center}
\vspace{5mm}

My passion for teaching is rooted in the belief that every student 
can succeed when complex subjects are made clear, relevant, and engaging. 
I am dedicated to demystifying the worlds of Physics, Mathematics, and Programming, 
helping students build confidence and develop powerful problem-solving skills. 
My goal is to create a learning environment where curiosity is sparked, and students 
from all backgrounds feel empowered to master challenging concepts.


\vspace{4mm}
\noindent\textbf{Teaching Methodology}
\begin{itemize}
    \item \textbf{Fostering an Inclusive and Empowering Environment:} I am committed to 
    cultivating a classroom where every student feels empowered to tackle challenging material, 
    ask questions freely, and realize their full potential. My experience with diverse student 
    populations has taught me the value of patience and clear communication. I strive to build 
    a supportive community where students feel secure enough to take intellectual risks and view 
    mistakes as vital learning opportunities.

    \item \textbf{Connecting Abstract Concepts to the Real World:} My approach is grounded in making 
    abstract theory tangible. In Physics and Math, this means connecting principles to students' lived 
    experiences, like using a roller coaster to explain energy conservation. In Computer Science, 
    it means demystifying algorithms and data structures by linking them to the technology students 
    use daily, from search engines to streaming services. This focus on real world application sparks 
    genuine curiosity across all disciplines.

    \item \textbf{Integrating Hands-On Programming and Computational Skills:} My background as a computational 
    physicist and open-source software developer provides a robust foundation for teaching Physics, Mathematics and Computer Science. 
    Beyond simply using computational tools, I am passionate about teaching the core principles of programming, 
    algorithmic thinking, and software design. My experience creating Python packages allows me to design hands-on, 
    project-based learning experiences that equip students with practical and high demand skills.

    \item \textbf{Promoting Active Learning and Dedicated Mentorship:} I believe that learning is fundamentally an 
    active, collaborative process. I design my classes to be interactive, incorporating group problem-solving and 
    lively discussion. My years in the Physics Help Center have reinforced my belief in the profound impact of 
    one-on-one mentorship. I see my role as a dedicated guide, committed to helping students build the confidence 
    and skills essential for their success.
\end{itemize}

\vspace{4mm}
I am enthusiastic about the opportunity to join an academic institution 
dedicated to excellence in education. I am eager to share my passion for 
Physics, Mathematics, and Programming with the next generation of thinkers, 
innovators, and problem solvers.

\vspace{5mm}
\noindent
\textbf{Abdul Saboor} \\
\href{mailto:asaboor@udel.edu}{asaboor@udel.edu} \\
\href{tel:+13027227047}{(302) 722-7047}


\end{document}