\documentclass[letter,11pt]{article}
\usepackage[left=0.8in,right=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black,
}

\urlstyle{same}
\titleformat{\section}{\large\bfseries\color{blue!60!black}}{}{0em}{} 

\begin{document}

\begin{minipage}{0.5\textwidth}
    \raggedright
    {\Large \textbf{ABDUL SABOOR}} \\
    Department of Physics and Astronomy, University of Delaware, Newark, DE 19716
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
    \raggedright
    \faGithub \quad \href{https://github.com/asaboor-gh}{asaboor-gh} \\
    \faLinkedin \quad \href{https://linkedin.com/in/asaboor-in}{asaboor-in} \\
    \faPhone \quad \href{tel:+13027227047}{(302) 722-7047} \\
    \faEnvelope \quad \href{mailto:asaboor@udel.edu}{asaboor@udel.edu}
\end{minipage}
\vspace{2mm}
\hrule
\vspace{5mm}

\noindent Data-focused researcher skilled in solving cutting-edge research problems in computational material science using Python (6+ years). Author of open-source tools for post-processing, analysis, and presentation in Jupyter. Experienced in managing projects end to end and collaborating with cross-functional partners. Basic hands-on experience with SQL and MongoDB.

\section{Education}
\begin{tabular}{p{3cm} p{12cm}}
    \textbf{2026} (expected) & Ph.D. Candidate in Physics, University of Delaware \\
    \textbf{2025} & M.S. in Physics, University of Delaware \\
    \textbf{2017} & M.Phil. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2015} & M.Sc. in Physics, Quaid-i-Azam University, Islamabad \\
    \textbf{2012} & B.Sc. in Mathematics \& Physics, University of Azad Jammu \& Kashmir \\
\end{tabular}

\section{Programming \& Research Experience}
\begin{itemize}
    \item Built \href{https://github.com/asaboor-gh/ipyvasp}{ipyvasp} to parse and post-process large VASP simulation outputs for electronic and structural properties of materials.
    \item Created \href{https://github.com/asaboor-gh/ipyslides}{ipyslides} to present live analyses and results inside Jupyter for talks and teaching.
    \item Building \href{https://github.com/asaboor-gh/dashlab}{dashlab} to create interactive dashboards in Jupyter for data exploration and visualization.
    \item Led end-to-end analysis alone and with collaborators: clarified questions, and solved research problems using Python.
    \item Collaborated with experimental and computational researchers to work on cutting-edge materials research including Bi incorporation in III-V alloys for mid-infrared applications and strain effects on electronic properties of 2D \& 3D materials.
\end{itemize}

\section{Technical \& Computational Skills}
\begin{itemize}
    \item \textbf{Programming:} Python (6+ years), MATLAB, Mathematica, Powershell
    \item \textbf{Data:} SQL and MongoDB (basic hands-on experience)
    \item \textbf{Visualization:} matplotlib, seaborn, plotly
    \item \textbf{Tools:} Git, Linux, Bash, Conda, Jupyter, VS Code, \LaTeX
\end{itemize}

\section{Teaching, Mentoring \& Communication}
\begin{itemize}
    \item Trained undergraduate students in coding for data analysis, experiment design, and instrumentation. Wrote step-by-step labs and rubrics. Ran multiple sections and office hours.
    \item Presented results to audiences with different backgrounds and produced clear documentation and procedures.
\end{itemize}

\section{Publications}
\begin{itemize}
    \item S. Nair, \textbf{A. Saboor}, et al., ``Engineering metal oxidation using epitaxial strain,'' \href{https://www.nature.com/articles/s41565-023-01397-0}{\textit{Nat. Nanotechnol.} (2023)}
    \item \textbf{A. Saboor}, S. Khalid, A. Janotti, ``Band-gap reduction and band alignments of dilute bismide III-V alloys,'' \href{https://arxiv.org/abs/2411.19257}{\textit{arXiv:2411.19257}} (2024)
\end{itemize}

\section{Conference Participations}
\begin{itemize}
    \item The 67$^{th}$ Electronic Materials Conference, Duke University NC, 2025
    \item PyCon US, Pittsburgh, 2025
    \item The Franklin Institute Awards Symposium, Temple University, 2025
    \item American Physical Society March Meetings, Las Vegas 2023 and Minneapolis 2024
    \item Workshop for density functional theory, Temple University, 2019
\end{itemize}

\section{Honors \& Awards}
\begin{itemize}
    \item University-funded presentation at the APS March Meeting on III-V semiconductor alloys (2023)
    \item World Federation of Scientists scholarship, Switzerland (2016)
    \item Scholarship offer for doctoral studies at \textit{Universidad Nacional Autónoma de México} (2015)
\end{itemize}

\section{References}
\textbf{Prof. Anderson Janotti} \\
Department of Materials Science and Engineering, University of Delaware \\
Email: \href{mailto:janotti@udel.edu}{janotti@udel.edu} \\
\vspace{2mm}

\noindent\textbf{Prof. Edward R. Lyman} \\
Department of Physics and Astronomy, University of Delaware \\
Email: \href{mailto:elyman@udel.edu}{elyman@udel.edu}
\end{document}