\documentclass[letter,11pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black,
}

\pagestyle{empty}

\begin{document}

\noindent
\textbf{Abdul Saboor} \\
Department of Physics and Astronomy \\
University of Delaware, Newark, DE 19716 \\
\href{mailto:asaboor@udel.edu}{asaboor@udel.edu} \\
\href{tel:+13027227047}{(302) 722-7047}

\vspace{5mm}

\noindent
\textbf{Re: Data Scientist Position at Databricks (Mountain View)}
\vspace{5mm}

\noindent
Dear Hiring Manager,

I am applying for the Data Scientist role at Databricks. I build reliable Python tools and analyze complex, data-driven research problems. I hold an M.S. in Physics and am completing a Ph.D. in Physics (expected 2025-2026). I am ready to contribute to impactful projects.

I work daily in Python for data wrangling, analysis, and modeling in computational semiconductor physics. Besides research, I authored \href{https://github.com/asaboor-gh/ipyvasp}{ipyvasp}, a post-processing tool for VASP calculations to analyze electronic and structural properties of materials, and \href{https://github.com/asaboor-gh/ipyslides}{ipyslides} for presenting workflows and results interactively in Jupyter. These projects show that I ship maintainable code, write clear documentation, and support users.

I have basic, hands-on experience with SQL and MongoDB from testing and small tasks. I rely on Python for most analysis and I am confident I can ramp up my use of SQL and databases quickly.
I manage projects end to end. I gather requirements, explore data, build baselines, and present insights. As a teaching assistant and mentor, I trained students in coding and data analysis.

Thank you for reviewing my application. I would welcome a chance to discuss how my coding, analysis, and communication skills can support your team.

\vspace{5mm}

\noindent
Sincerely, \\
Abdul Saboor
\end{document}